\documentclass[a4paper]{article}
\usepackage{hyperref}
\usepackage{enumitem}
\setlist{nosep}
\raggedright
\input{glyphtounicode}
\pdfgentounicode=1
\usepackage[left=0.5in,top=0.25in,right=0.5in,bottom=0.25in]{geometry}
% \usepackage{tgschola}
\usepackage[T1]{fontenc}
\usepackage{titlesec}

% ----------- Config -----------

\hypersetup {
    colorlinks   = true, %Colours links instead of ugly boxes
    urlcolor     = blue, %Colour for external hyperlinks
    linkcolor    = blue, %Colour of internal links
}

% ----------- End of Config -----------

% ----------- Definitions -----------
    
\newcommand{\bulletSep} { \vspace{1.5mm} }

\newcommand{\sectionSep} { \vspace{3mm} }

\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-15pt} \hrulefill \\
}

\newcommand{\header} [1] {
    {\hspace*{-18pt}\vspace*{6pt} {
        \fontfamily{qcs}\selectfont \large \scshape #1
    }}
    \vspace*{-6pt} \lineunder
    \vspace{0.5mm}
}

\newcommand{\educationItem}[5]{
    \textbf{#1}\hfill #2\\
    #3, \textit{#4} \hfill #5\\
}

\newcommand{\experienceItem}[5]{
    \textbf{#1} \hfill #2 \\
    \textit{#3} \hfill #4 \\
    \begin{itemize}
        #5
    \end{itemize}
}

\newcommand{\projectItem}[5]{
    {\textbf{#1}} {(\sl #2)}\hfill
    \ifx&#3&%
    % #3 is empty
    \href{#4}{Github}\\
    \else
    % #3 is nonempty
    \href{#3}{Live Preview} | \href{#4}{Github}\\
    \fi
    \begin{itemize}
        #5
    \end{itemize}
}


% ----------- End of definitions -----------

\begin{document}

% ----------- Profile -----------

\begin{center}
    {\Huge \scshape \fontfamily{qcs}\selectfont Akshat Aggarwal}\\
    \vspace{1mm}
    % \href{}{Portfolio} $\cdot$
    LinkedIn: \href{https://www.linkedin.com/in/akshataggarwal1411/}{akshataggarwal1411} $\cdot$
    Github: \href{https://github.com/AkshatAggarwal14}{AkshatAggarwal14} $\cdot$
    Codeforces: \href{https://codeforces.com/profile/master._.mind}{master.\_.mind} $\cdot$
    Codechef: \href{https://www.codechef.com/users/master_mind14}{master\_mind14} \\
    \vspace{0.5mm}
    Email: \href {mailto:akshataggarwal1411@gmail.com}{akshataggarwal1411@gmail.com} $\cdot$ Mobile: (+91) 78762 12728\\
\end{center}

\vspace{-3mm}

% ----------- Education -----------

\header{Education}

\educationItem{National Institute of Technology, Hamirpur}{Hamirpur}{Bachelor of Technology, Computer Science \& Enginnering}{CGPA: 9.69}{Dec 2020 - Present}
\bulletSep

\educationItem{The Scholars' Home}{Paonta Sahib}{Higher Secondary ($12^{th}$)}{Percentage: 97}{Apr 2019 - Mar 2020}
\sectionSep

% ----------- Work Experience -----------

\header{Work Experience}

\experienceItem{Coding Ninjas}{Remote}{Technical Content Writer Intern}{Mar 2023 - Jun 2023}{
    \item Created high-quality content covering a wide range of programming languages, frameworks, and tools.
    \item Authored and edited technical blog posts, tutorials, etc., aimed at helping students learn and improve.
}
\bulletSep

\experienceItem{Coding Shuttle}{Remote}{Problem Setter}{Feb 2023 - Mar 2023}{
    \item Generated test cases and optimal solutions for problems based on Data Structures and Algorithms.
}
\sectionSep

% ----------- Volunteer Experience -----------

\header{Volunteer Experience}

\experienceItem{CSEC NITH}{NIT Hamirpur}{Coordinator}{Apr 2021 - Present}{
    \item Designed problems and wrote editorials for monthly programming contest, Heuristics.
    \item Volunteered on `Software Freedom Day', promoted FOSS and installed linux distributions on 50+ PCs.
    \item Conducted programming meets on various topics.
}
\bulletSep

\experienceItem{CodeChef NITH Chapter}{NIT Hamirpur}{Chapter Leader}{Jul 2021 - Jan 2022}{
    \item Organized workshops on topics `Introduction to Competitive Programming' and `STL' (100+ attendees each).
    \item Conducted numerous programming contests like `Regular Contest 1', `CP Liftoff' etc (50+ participants each).
}
\sectionSep

% ----------- Projects -----------

\header{Projects}

\projectItem{RFID Attendance System}{Node.js, Express, MongoDB, React, Arduino}{}{https://github.com/AkshatAggarwal14/RFID-Attendance-system}{
    \item Developed an attendance tracking system that allows users to register their attendance by scanning RFID cards using an RFID reader.
    \item Established seamless serial communication between the Arduino board and Node.js.
}
\bulletSep

\projectItem{Paint Application}{C++, WinBGIm Graphics Library}{}{https://github.com/Sahil-187/Paint-Application}{
    \item Created a comprehensive paint application with \textbf{user-friendly graphical interface}.
    \item \textbf{Features}: Save as JPEG file, Color Palette, Size options, etc.
    \item \textbf{Tools}: Brush, Flood Fill, Rectangle, Circle, Line, etc.
}
\bulletSep

\projectItem{Sort Visualizer}{p5.js, CSS3, HTML5}{https://akshataggarwal14.github.io/Sorting-Algorithms/}{https://github.com/AkshatAggarwal14/Sorting-Algorithms/}{
    \item Developed a web application to visualize various sorting algorithms.
    \item Implemented Interactive UI features, including the selection of sorting algorithms and adjustable parameters for visualization size and speed.
}\bulletSep

\projectItem{React Wordle}{React, CSS3}{https://wordle-with-react.netlify.app/}{https://github.com/AkshatAggarwal14/react-wordle}{
    \item Created a web-based word-guessing game where users can guess a hidden word by entering their guesses.
    \item Implemented animations and media queries to enhance the user experience.
}
\sectionSep

% ----------- Achievements -----------

\header{Achievements}
\begin{itemize}
    \item \textbf{\href{https://www.codechef.com/users/master_mind14}{6 Star}} (Max Rating - 2211) on Codechef (\textbf{380th out of 200K} Indian users).
    \item \textbf{\href{https://codeforces.com/profile/master._.mind}{Expert}} (Max Rating - 1671) on Codeforces.
    \item Top \textbf{\href{https://leetcode.com/AkshatAggarwal14/}{1.9\%}} on Leetcode (Max Rating - 2079).
    \item Ranked \textbf{\href{https://www.codechef.com/rankings/COOK139B?itemsPerPage=100&order=asc&page=1&search=master_mind14&sortBy=rank}{30th}} globally out of 2900+ participants in \textbf{March Cook-Off 2022} Div-2.
    \item Ranked \textbf{\href{https://codeforces.com/contest/1729/standings/participant/140098304\#p140098304}{143rd}} globally (39th in India) out of 18K+ participants in \textbf{Codeforces Round 820}.
    \item Ranked \textbf{\href{https://clist.by/standings/kick-start-round-g-31261744/?find_me=45689030}{318th}} out of 12K+ participants in \textbf{Google Kickstart} 2022 Round G.
\end{itemize}
\sectionSep

% ----------- Skills -----------

\header{Skills}
% [t] option means top
\begin{minipage}[t]{0.6\textwidth}
    % Column 1
    C/C++, Python, Javascript, Go\\
    \textbf{Databases:} MySQL, MongoDB\\
    \textbf{Others:} Bash, Markdown, \LaTeX, Data Structures and Algorithms
\end{minipage}
\hfill
\begin{minipage}[t]{0.33\textwidth}
    % Column 2
    \textbf{Frameworks:} React, Node, Express\\
    \textbf{Tools:} Git, GNU/Linux
\end{minipage}
\sectionSep

% ----------- Coursework -----------
\header{Coursework}
Data Structures \& Algorithms,
Operating Systems,
Object Oriented Programming,
Computer Organization \& Architecture,
Database Management Systems,
Compiler Design,
Distributed Systems,
Computer Networks

\end{document}
